---
title: "Final Project Quarto"
author: "Julia Singer"
format: html
editor: visual
---

```{r}
#| message: false

library(gtsummary)
library(tidyverse)
library(broom)

agegap_cols <- c("movie_name", "release_year", "director",
								 "age_difference", "couple_number", "actor_1_name",
								 "actor_2_name", "character_1_gender", "character_2_gender",
								 "actor_1_birthdate", "actor_2_birthdate", "actor_1_age",
								 "actor_2_age")

agegap <- read_csv(here::here("age_gaps.csv"),
col_names = agegap_cols)
```

```{r}
agegap = subset(agegap, select = -c(couple_number, actor_1_birthdate,
																		actor_2_birthdate, age_difference))

agegap$character_1_gender <- ifelse(agegap$character_1_gender
																		%in% c("man"),1,0)
agegap$character_2_gender <- ifelse(agegap$character_2_gender
																		%in% c("man"),1,0)
```

```{r}
#| warning: false

agegap$actor_1_age <- as.numeric(agegap$actor_1_age)

agegap$actor_2_age <- as.numeric(agegap$actor_2_age)

agegap$age_difference <- (agegap$actor_1_age - agegap$actor_2_age)
```

```{r}
#| label: tbl-1
#| tbl-cap: Summary of Actor Ages and Gender 

tbl_summary(
	agegap,
	by = character_1_gender,
	include = c(actor_2_age, actor_1_age,
							character_2_gender),
	label = list(
		actor_2_age ~ "Age of Actor 2",
		actor_1_age ~ "Age of Actor 1",
		character_1_gender ~ "Gender Identity of Character 1",
		character_2_gender ~ "Gender Identity of Character 2"
		),
missing_text = "Missing")

table_summ <- tbl_summary(
	agegap,
	by = character_1_gender,
	include = c(actor_2_age, actor_1_age,
							character_2_gender),
missing_text = "Missing")

inline_text(table_summ, variable = "actor_2_age", 
						column = "0")

```

In @tbl-1, the median age of female actors recorded as Actor 2 is `r inline_text(table_summ, variable = "actor_2_age", column = "0")`

```{r}

actor1age_table <- tbl_uvregression(
	agegap,
	y = actor_1_age,
	include = c(actor_2_age, age_difference, character_1_gender,
							character_2_gender),
method = lm)

```

```{r}
agediffvalue <- inline_text(actor1age_table, variable = "age_difference")

avgact1age <- mean(agegap$actor_1_age, na.rm = TRUE)

avgact2age <- mean(agegap$actor_2_age, na.rm = TRUE)
```

The average age of Actor 1 actors is `r round(avgact1age, 1)`

The average age of Actor 2 actors is `r round(avgact2age, 1)`

```{r}
#| label: fig-hist
#| fig-cap: Histogram of Age Difference Across Actor Sets

hist(agegap$age_difference)

```

In @fig-hist, the relationship between number of actors and age difference is inversely related. The age difference between Actors 1 and 2 increases as the frequency decreases.

```{r}
mean_age <- function(age_difference) {
	t <- length(age_difference)
	mean <- sum(age_difference, na.rm = TRUE)/t
	return(mean)
}

mean_age(agegap$age_difference)
```

```         
```
